Hierarchical Inference of the Intrinsic Ellipticity Distribution of Galaxies during Weak Lensing Analysis

### 2013-03-29 docs/ms.tex
Update ms.tex

Our approach is to use an exceedingly flexiable model for intrinsic shape distribution,and assumes all the galaxies in different
patches abeys such an distribution.Then we can calculate the joint likelihood of both shpape distribution parameters and shear in differ
With a classical Gibbs MCMC sampler we are able to sample their posteior distriibution.After marginalizing the shape parameters, we can
obtain the posterior distribution of shear,which we are interested in.

>>>>

Our approach is to use an exceedingly flexible model for intrinsic shape distribution,and assumes all the galaxies in different
patches abeys such a distribution.Then we can calculate the joint likelihood of  shpape distribution parameters and shear in differ
With a classical Gibbs MCMC sampler we are able to sample their posteior distriibution.After marginalizing the shape parameters, we can
obtain the posterior distribution of shear,which we are interested in.
